Truthfulness Verification System

### 2011-05-04 trunk/proposal/paper.tex
updated grammer
alg 1 example done

Now for each k-gram we find relevant wikipedia page. We will not get any wikipedia page for irrelevant k-gram combination.  Moreover, We may get a page directly or we may need to disambiguate. Following are the all relevant pages. The False in the second column means there is no ambiguation and True means we need to disambiguate.

@@

Now, we need to count word overlap for each of the pages for les paul, adolph rickenbacker, leo with all pages for the topic unit and take sum of the overlap to produce the ranking of alternate units

>>>>

Now for each k-gram we find relevant wikipedia page. We will not get any wikipedia page for irrelevant k-gram.  Moreover, we may get a page directly or we may need to disambiguate. Following are the all relevant pages. The False in the second column means there is no ambiguation and True means we need to disambiguate.

@@

Now, we need to count word overlap for each of the pages for les paul, adolph rickenbacker, leo with all pages for the topic unit and take sum of the overlap to produce the ranking of alternate units. So we generate bag of words for pages corresponding to all alternative units and also all the pages for the topic unit.

Finally, for each alternate unit page, we count word overlap between alternate unit page and all topic unit pages and take sum of them. Now, we have a value associated with each alternate units that we are using for the ranking of the alternate units. Total count value for all alternate units and corresponding ranking is given below:

231 Les Paul \\
143 Adolph Rickenbacker \\
0 Leo

From this ranking we can clearly state that Les Paul is the correct answer.
